Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
removing comments.
indenting for readablity.
adding a comment.

\begin{quote}
    TBD: ``Section'' to ``section''
\end{quote}

@@

\begin{quote}
\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.

    \emph{kazu: I guess that it's enough to describe this in the Implementation Section.}
\end{itemize}
\end{quote}

>>>>

\begin{quote}
    TBD: ``Section'' to ``section''

kazu: ``Section X.Y'' is perfect English, i.e. a proper noun.
      ``The following three sections'' is also perfect, i.e. a ordinal noun.
\end{quote}

@@
